---
title: "Intro to Geospatial Visualization with leaflet in R"
author: "Ashirwad Barnwal"
date: "11/26/2020"
output: 
  xaringan::moon_reader:
    lib_dir: libs
    css: ["kunoichi", "ninjutsu"]
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include = FALSE}
library(leaflet)
library(rnaturalearth)
library(knitr)
library(emo)

asian_countries <- ne_countries(
  continent = "asia", 
  returnclass = "sf"
)
```

---

layout: false
class: bg-main3 split-30

.column[

]

.column.slide-in-right[.content.vmiddle[

.sliderbox.shade_main.pad1[
.font5[Legends]
]

]]

---

class: split-two white

.column.bg-main1[.content[

# Legend for .yellow[colorNumeric]-based palette

```{r legend-num-pal, eval = FALSE}
leaflet(asian_countries) %>%
  addPolygons(
    stroke = FALSE,
    color = ~num_pal(gdp_md_est),
    fillOpacity = 1,
    smoothFactor = 0.2
  ) %>%
  addLegend(
    position = "bottomright",
    pal = num_pal,
    values =  ~gdp_md_est,
    opacity = 1,
    labFormat = labelFormat(prefix = "$"),
    title = "Est. GDP (2010)"
  )
```

]]

.column.bg-main3[.content.vmiddle[

```{r legend-num-pal-out, ref.label = "legend-num-pal", echo = FALSE, warning = FALSE, out.width = "100%"}

```

]]

---

class: split-two white

.column.bg-main1[.content[

# Legend for .yellow[colorQuantile]-based palette

```{r legend-q-pal, eval = FALSE}
leaflet(asian_countries) %>%
  addPolygons(
    stroke = FALSE,
    color = ~q_pal(gdp_md_est),
    fillOpacity = 1,
    smoothFactor = 0.2
  ) %>%
  addLegend(
    pal = q_pal,
    values = ~gdp_md_est,
    opacity = 1
  )
```

]]

.column.bg-main3[.content.vmiddle[

```{r legend-q-pal-out, ref.label = "legend-q-pal", echo = FALSE, warning = FALSE, out.width = "100%"}

```

]]

---

class: split-40 white

.column.bg-main1[.content.vmiddle.center[

## Want to learn more about the .yellow[addLegend] function?  

## Check `r ji("point_right")`

]]

.column[.content.vmiddle[

```{r add-legend-doc, echo = FALSE}
include_url(
  "https://www.rdocumentation.org/packages/leaflet/versions/2.0.3/topics/addLegend",
  height = "600px"
)
```

]]









